### 2019-05-02 2-Chapters/3-Chapter/chapter3.tex
Almost done for text for chapter 3. I'm still not sure if I want to launch, copy-paste and comment on these simulations... What do they really give for the reader??

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.95\linewidth]{exampleOfRewards.pdf}
	\caption{Histogram of $10000$ \iid{} rewards obtained from three arms with a Gaussian distribution truncated to $[0,1]$, of respective means $0.1$, $0.5$ and $0.9$.}
	\label{fig:3:exampleOfRewards}
\end{figure}

@@

\subsection{Dependencies}

@@

Since $2017$ and $2018$, SMPyBandits is using the free version of two online continuous integration (CI) service, to automatically build and host the documentation, and to automatically test the library on some numerical simulations.
%
These CI services are free for open-source work, and are both triggered whenever a modification of the codebase is sent to the hosting platform (\ie, GitHub).

@@

-- In \cite{Besson2018ALT} and in Chapter~\ref{chapter:5} below, we used SMPyBandits for all the simulations for multi-player bandit algorithms\footnote{~See the page \texttt{\href{https://SMPyBandits.GitHub.io/MultiPlayers.html}{SMPyBandits.GitHub.io/MultiPlayers.html}} on the documentation.}. We designed the two \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.RandTopM.html}{RandTopM}} and \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.MCTopM.html}{MCTopM}} algorithms and proved than they enjoy logarithmic regret in the usual setting, and outperform significantly the previous state-of-the-art solutions (\ie, \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.rhoRand.html}{rhoRand}}, \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MEGA.html}{MEGA}} and \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MusicalChair.html}{MusicalChair}}).

-- In \cite{Besson2018DoublingTricks} (quickly presented in Appendix~\ref{app:2:DoublingTricks}), we used SMPyBandits to illustrate and compare different "doubling trick" schemes\footnote{~See the page \texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}} on the documentation.}. and lots of bibliographic referencesIn sequential learning, an algorithm is anytime if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any non-anytime algorithm to an anytime variant is the ``Doubling Trick'': start with an horizon $T_0\in\mathbb{N}^*$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to conserve minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to conserve a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to conserve logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can conserve minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

-- In \cite{Besson2019GLRT} and \cite{Besson2019Gretsi}, and in Chapter~\ref{chapter:6} below, we used SMPyBandits for piece-wise stationary MAB models (only for the single-player case). We illustrate and compare different algorithms designed for this family of non-stationary problems\footnote{~See the page \texttt{\href{https://SMPyBandits.GitHub.io/NonStationary.html}{SMPyBandits.GitHub.io/NonStationary.html}} on the documentation.}.
We designed the \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.GLR_UCB.html}{GLRklUCB}} policy, and implemented most of the policies from state-of-the-art research on passively or active adaptive policies, both adversarial- or stochastic-based, designed to tackle the piece-wise stationary MAB problems.
We also implemented a large benchmark of different problems.

@@

>>>>

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=0.75\linewidth]{exampleOfRewards.pdf}
	\caption{Histogram of $10000$ \iid{} rewards obtained from three arms with a Gaussian distribution truncated to $[0,1]$, of respective means $0.1$, $0.5$ and $0.9$.}
	\label{fig:3:exampleOfRewards}
\end{figure}

@@

\subsection{Dependencies}
\label{sub:3:dependencies}

@@

Since $2017$ and $2018$, SMPyBandits is using two online continuous integration (CI) service, to automatically build and host the documentation, and to automatically test the library on some numerical simulations.
%
These CI services are free for open-source works, and are both triggered whenever a modification of the codebase is sent to the hosting platform (\ie, GitHub).

@@

-- In \cite{Besson2018ALT} and in Chapter~\ref{chapter:5} below, we used SMPyBandits for all the simulations for multi-player bandit algorithms\footnote{~Similarly, see the page \texttt{\href{https://SMPyBandits.GitHub.io/MultiPlayers.html}{SMPyBandits.GitHub.io/MultiPlayers.html}} on the documentation.}. We designed the two \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.RandTopM.html}{RandTopM}} and \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.MCTopM.html}{MCTopM}} algorithms and proved than they enjoy logarithmic regret in the usual setting, and outperform significantly the previous state-of-the-art solutions (\ie, \texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.rhoRand.html}{rhoRand}}, \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MEGA.html}{MEGA}} and \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MusicalChair.html}{MusicalChair}}).

-- In \cite{Besson2018DoublingTricks} (quickly presented in Appendix~\ref{app:2:DoublingTricks}), we used SMPyBandits to illustrate and compare different "doubling trick" schemes\footnote{~Similarly, see the page \texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}} on the documentation.}. and lots of bibliographic referencesIn sequential learning, an algorithm is anytime if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any non-anytime algorithm to an anytime variant is the ``Doubling Trick'': start with an horizon $T_0\in\mathbb{N}^*$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to conserve minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to conserve a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to conserve logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can conserve minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

-- In \cite{Besson2019GLRT} and \cite{Besson2019Gretsi}, and in Chapter~\ref{chapter:6} below, we used SMPyBandits for piece-wise stationary MAB models (only for the single-player case). We illustrate and compare different algorithms designed for this family of non-stationary problems\footnote{~Similarly, see the page \texttt{\href{https://SMPyBandits.GitHub.io/NonStationary.html}{SMPyBandits.GitHub.io/NonStationary.html}} on the documentation.}.
We designed the \texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.GLR_UCB.html}{GLRklUCB}} policy, and implemented most of the policies from state-of-the-art research on passively or active adaptive policies, both adversarial- or stochastic-based, designed to tackle the piece-wise stationary MAB problems.
We also implemented a large benchmark of different problems.

@@

In this section, we use the SMPyBandits library to compare experimentally various state-of-the-art single-player algorithms on different kinds of multi-armed bandit problems.
First, we detail the list of $9$ different algorithms that we compare, and the different problems on which they are all tested.
We give the results of the numerical experiments, in terms of mean regret at the end of the experiment of different horizons $T$.
Additional results in terms of real measurements of time and memory are given and discussed in the next Section~\ref{sec:3:timeAndMemoryCosts}.

Finally, we give some observations on the results, and the main take-away message of this section is the following: in all the rest of this thesis, we focus on using the simple \UCB{} algorithm when simplicity is favored, \ie, in the more applied Chapter~\ref{chapter:4}, and the \klUCB{} algorithm when efficiency is favored, \ie, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}.

\subsection{Experimental setup: algorithms and problems}

\paragraph{List of algorithms}

We consider the nine following algorithms. For each of them, we give a bibliographic reference, that corresponds to the most recent article studying it and not the first one which introduced it.
We give the chosen tuning of the parameters, for parametric algorithms.
Algorithms that are not anytime use the exact value of the horizon $T$, and when increasing values of $T$ are studied for the same problem, of course they use the correct successive values.
We also give the name of the corresponding class in the \texttt{Policies} module in SMPyBandits.

% FIXME order from oldest to most recent, and simplest to more complex

\begin{itemize}
    \item Algorithm 1 is
    an $\varepsilon$-greedy algorithm, as described in \cite{Bubeck12}, using $\varepsilon_t = \varepsilon_0 / t$, and $\varepsilon_0 = 0.1$ (chosen arbitrarily) (\texttt{EpsilonDecreasing}).

    \item Algorithm 2 is
    an Explore-then-Commit algorithm from \cite{GarivierETC2016}, that knows the horizon, and a lower-bound on the gap between arms (chosen arbitrarily as $\delta=0.01$, valid for all problems) (\texttt{ETC\_KnownGap}).

    \item Algorithm 3 is
    $\mathrm{Exp}3^{++}$ from \cite{Seldin17}, using $\alpha=3$ and $\beta=256$ as advised (\texttt{Exp3PlusPlus}).

    \item Algorithm 4 is
    $\UCB_1$ from \cite{Auer02}, using $\alpha=1$ (\texttt{UCB}).

    \item Algorithm 5 is
    \klUCB{} from \cite{KLUCBJournal}, using the Bernoulli KL divergence and the corresponding \klUCB{} indexes, implemented as \texttt{kullback.klucbBern} (\texttt{klUCB}).

    \item Algorithm 6 is
    Thompson sampling from \cite{Kaufmann12Thompson}, using a Beta prior and posterior, initially uniform (\ie, $\mathrm{Beta}(1,1)$) (\texttt{Thompson}).

    \item Algorithm 7 is
    Bayes-UCB from \cite{Kaufmann12BUCB}, using a Beta prior and posterior, initially uniform (\ie, $\mathrm{Beta}(1,1)$) (\texttt{BayesUCB}).

    \item Algorithm 8 is
    AdBandits from \cite{Truzzi13}, using $\alpha=1$ (\texttt{AdBandits}).

    \item Algorithm 9 is
    BESA (Best Empirical Sampled Average) from \cite{Baransi2014}, using a binary tournament implement in a naive but efficient way (not using recursive functions) (\texttt{BESA} with \texttt{''non\_recursive''=True}).
\end{itemize}

In the results presented in the main text of this chapter, we focus on the most well known algorithms, and two others that are efficient but less known (AdBandits and BESA).
We present in Appendix~\ref{sub:3:additionalExperiments} seven other algorithms, being more recent (from $2016$, $3$ from $2018$ and $2$ from $2019$) but are usually more complex, or are based on a different point-of-view.
We include numerical results for these other algorithms as well, to justify empirically that despite their respective qualities, and despite being efficient, it is reasonable to focus on \UCB{} and \klUCB{} algorithms in the rest of this thesis.

\paragraph{Two different problems}

We consider two different problems, that are described here for a generic value of $K \geq 2$ the number of arms.
For simplicity, we focus on Bernoulli distributed arms, even if similar results were observed for other distributions, in particular for truncated or untruncated Gaussian distributions.

\begin{itemize}
    \item \textbf{Problem 1} considers $K$ arms of equally spaced means, in $[0,1]$.
    It uses a minimum mean of $0.05$ and a maximum mean of $0.95$.
    For instance, for $K=2$, $\bm{\mu}=[0.05, 0.95]$ and for $K=5$, $\bm{\mu} = [0.05, 0.275, 0.5, 0.725, 0.95]$.

    \item \textbf{Problem 2} takes another approach. Instead of simulating $1000$ times the same problem, it generates a new random problem for each independent run.
    It considers a randomly generated vector of means, each being sampled uniformly at random in $[0,1]$, with a minimum gap of $\Delta^{\min}$, $\bm{\mu} \sim \cE(\Delta^{\min},\mu_{\min},\mu_{\max})$, as well as minimum and maximum values of $\mu_{\min}$ and $\mu_{\max}$.
    This space $\cE_{\Delta^{\min}}$ is defined as $\{ \bm{\mu} \in [\mu_{\min}, \mu_{\max}]^K : \min_{k\neq k'} |\mu_k - \mu_{k'}| \geq \Delta^{\min} \}$.
    We use $\mu_{\min} = \Delta^{\min}$ and $\mu_{\max} = 1 - \Delta^{\min}$,
    and the value used for $\Delta^{\min}$ is $0.1$ for $K \leq 3$ (for ``easy'' problems), and $\frac{1}{3 K}$ for $K \geq 5$ (for ``harder'' problems).
    % 0.1 if NB_ARMS <= 5 else 1. / (3 * NB_ARMS)
\end{itemize}

\paragraph{Other parameters of the experiments}

We consider increasing values for the horizon, $T=1000$, $T=5000$, $T=10000$ and $T=50000$.  % FIXME update if needed?
We consider as well an increasing number of arms, $K=2$, $K=5$, $K=9$, $K=20$ and $K=50$.  % FIXME update if needed?
For all experiments, we run $N=1000$ independent simulations.  % FIXME update if needed?

\subsection{Experiments results}

We give in the tables below the results of the experiments. For the two different problems and different values of $T$ and $K$, we give the mean $\pm 1$ standard-variation of the empirical regret $R_T$ obtained by the different algorithms at the end of the experiments.
Tables~\ref{table:3:meanRegret_problem1} is for the fixed-gap \textbf{problem 1}
and \ref{table:3:meanRegret_problem2}  is for the randomly generated \textbf{problem 2}.
Each column corresponds to one value of $T$, and each line corresponds to one algorithm.
For each cell, we report successive values that correspond to the successive values of the number of arms $K$.

\TODOL{FIXME launch these experiments, for a very short number of repetitions N=4, and if I'm happy about the results and if they are easily copied-and-pasted here, then launch with N=100 or N=1000 depending on the running

% DEBUG=True; NOPLOTS=False; SAVEALL=False; for N in 4 100 1000; do for BAYES in False True; do for T in 1000 5000 10000 50000; do for K in 2 5 10 20 50; do debut=$(date); DEBUG=$DEBUG NOPLOTS=$NOPLOTS SAVEALL=$SAVEALL N=$N N_JOBS=-1 T=$T K=$K BAYES=$BAYES make --noFreeSMS single && cp logs/main_py3_log.txt logs/main_py3_log__N${N}_BAYES${BAYES}_T{T}_K{K}.txt && FreeSMS.py "Expérience commencée ${debut} terminée, avec N=${N}, BAYES=${BAYES}, T=${T}, K=${K}." ; done; done; done; done time.}

\begin{table}[!t]
\begin{footnotesize}
    \centering
    \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
    \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
        & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
        \hline
        $\varepsilon$-greedy &
            $R^{1}_{T_1,K_1} = 0 \pm 0$
                $R^{1}_{T_1,K_2} = 0 \pm 0$
                $R^{1}_{T_1,K_3} = 0 \pm 0$
                $R^{1}_{T_1,K_4} = 0 \pm 0$
                $R^{1}_{T_1,K_5} = 0 \pm 0$ &
            $R^{1}_{T_2,K_1} = 0 \pm 0$
                $R^{1}_{T_2,K_2} = 0 \pm 0$
                $R^{1}_{T_2,K_3} = 0 \pm 0$
                $R^{1}_{T_2,K_4} = 0 \pm 0$
                $R^{1}_{T_2,K_5} = 0 \pm 0$ &
            $R^{1}_{T_3,K_1} = 0 \pm 0$
                $R^{1}_{T_3,K_2} = 0 \pm 0$
                $R^{1}_{T_3,K_3} = 0 \pm 0$
                $R^{1}_{T_3,K_4} = 0 \pm 0$
                $R^{1}_{T_3,K_5} = 0 \pm 0$ &
            $R^{1}_{T_4,K_1} = 0 \pm 0$
                $R^{1}_{T_4,K_2} = 0 \pm 0$
                $R^{1}_{T_4,K_3} = 0 \pm 0$
                $R^{1}_{T_4,K_4} = 0 \pm 0$
                $R^{1}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Explore-then-Commit &
            $R^{2}_{T_1,K_1} = 0 \pm 0$
                $R^{2}_{T_1,K_2} = 0 \pm 0$
                $R^{2}_{T_1,K_3} = 0 \pm 0$
                $R^{2}_{T_1,K_4} = 0 \pm 0$
                $R^{2}_{T_1,K_5} = 0 \pm 0$ &
            $R^{2}_{T_2,K_1} = 0 \pm 0$
                $R^{2}_{T_2,K_2} = 0 \pm 0$
                $R^{2}_{T_2,K_3} = 0 \pm 0$
                $R^{2}_{T_2,K_4} = 0 \pm 0$
                $R^{2}_{T_2,K_5} = 0 \pm 0$ &
            $R^{2}_{T_3,K_1} = 0 \pm 0$
                $R^{2}_{T_3,K_2} = 0 \pm 0$
                $R^{2}_{T_3,K_3} = 0 \pm 0$
                $R^{2}_{T_3,K_4} = 0 \pm 0$
                $R^{2}_{T_3,K_5} = 0 \pm 0$ &
            $R^{2}_{T_4,K_1} = 0 \pm 0$
                $R^{2}_{T_4,K_2} = 0 \pm 0$
                $R^{2}_{T_4,K_3} = 0 \pm 0$
                $R^{2}_{T_4,K_4} = 0 \pm 0$
                $R^{2}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\mathrm{Exp}3^{++}$ &
            $R^3_{T_1,K_1} = 0 \pm 0$
                $R^3_{T_1,K_2} = 0 \pm 0$
                $R^3_{T_1,K_3} = 0 \pm 0$
                $R^3_{T_1,K_4} = 0 \pm 0$
                $R^3_{T_1,K_5} = 0 \pm 0$ &
            $R^3_{T_2,K_1} = 0 \pm 0$
                $R^3_{T_2,K_2} = 0 \pm 0$
                $R^3_{T_2,K_3} = 0 \pm 0$
                $R^3_{T_2,K_4} = 0 \pm 0$
                $R^3_{T_2,K_5} = 0 \pm 0$ &
            $R^3_{T_3,K_1} = 0 \pm 0$
                $R^3_{T_3,K_2} = 0 \pm 0$
                $R^3_{T_3,K_3} = 0 \pm 0$
                $R^3_{T_3,K_4} = 0 \pm 0$
                $R^3_{T_3,K_5} = 0 \pm 0$ &
            $R^3_{T_4,K_1} = 0 \pm 0$
                $R^3_{T_4,K_2} = 0 \pm 0$
                $R^3_{T_4,K_3} = 0 \pm 0$
                $R^3_{T_4,K_4} = 0 \pm 0$
                $R^3_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\UCB_1$ &
            $R^{4}_{T_1,K_1} = 0 \pm 0$
                $R^{4}_{T_1,K_2} = 0 \pm 0$
                $R^{4}_{T_1,K_3} = 0 \pm 0$
                $R^{4}_{T_1,K_4} = 0 \pm 0$
                $R^{4}_{T_1,K_5} = 0 \pm 0$ &
            $R^{4}_{T_2,K_1} = 0 \pm 0$
                $R^{4}_{T_2,K_2} = 0 \pm 0$
                $R^{4}_{T_2,K_3} = 0 \pm 0$
                $R^{4}_{T_2,K_4} = 0 \pm 0$
                $R^{4}_{T_2,K_5} = 0 \pm 0$ &
            $R^{4}_{T_3,K_1} = 0 \pm 0$
                $R^{4}_{T_3,K_2} = 0 \pm 0$
                $R^{4}_{T_3,K_3} = 0 \pm 0$
                $R^{4}_{T_3,K_4} = 0 \pm 0$
                $R^{4}_{T_3,K_5} = 0 \pm 0$ &
            $R^{4}_{T_4,K_1} = 0 \pm 0$
                $R^{4}_{T_4,K_2} = 0 \pm 0$
                $R^{4}_{T_4,K_3} = 0 \pm 0$
                $R^{4}_{T_4,K_4} = 0 \pm 0$
                $R^{4}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        \klUCB{} &
            $R^{5}_{T_1,K_1} = 0 \pm 0$
                $R^{5}_{T_1,K_2} = 0 \pm 0$
                $R^{5}_{T_1,K_3} = 0 \pm 0$
                $R^{5}_{T_1,K_4} = 0 \pm 0$
                $R^{5}_{T_1,K_5} = 0 \pm 0$ &
            $R^{5}_{T_2,K_1} = 0 \pm 0$
                $R^{5}_{T_2,K_2} = 0 \pm 0$
                $R^{5}_{T_2,K_3} = 0 \pm 0$
                $R^{5}_{T_2,K_4} = 0 \pm 0$
                $R^{5}_{T_2,K_5} = 0 \pm 0$ &
            $R^{5}_{T_3,K_1} = 0 \pm 0$
                $R^{5}_{T_3,K_2} = 0 \pm 0$
                $R^{5}_{T_3,K_3} = 0 \pm 0$
                $R^{5}_{T_3,K_4} = 0 \pm 0$
                $R^{5}_{T_3,K_5} = 0 \pm 0$ &
            $R^{5}_{T_4,K_1} = 0 \pm 0$
                $R^{5}_{T_4,K_2} = 0 \pm 0$
                $R^{5}_{T_4,K_3} = 0 \pm 0$
                $R^{5}_{T_4,K_4} = 0 \pm 0$
                $R^{5}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Thompson sampling &
            $R^{6}_{T_1,K_1} = 0 \pm 0$
                $R^{6}_{T_1,K_2} = 0 \pm 0$
                $R^{6}_{T_1,K_3} = 0 \pm 0$
                $R^{6}_{T_1,K_4} = 0 \pm 0$
                $R^{6}_{T_1,K_5} = 0 \pm 0$ &
            $R^{6}_{T_2,K_1} = 0 \pm 0$
                $R^{6}_{T_2,K_2} = 0 \pm 0$
                $R^{6}_{T_2,K_3} = 0 \pm 0$
                $R^{6}_{T_2,K_4} = 0 \pm 0$
                $R^{6}_{T_2,K_5} = 0 \pm 0$ &
            $R^{6}_{T_3,K_1} = 0 \pm 0$
                $R^{6}_{T_3,K_2} = 0 \pm 0$
                $R^{6}_{T_3,K_3} = 0 \pm 0$
                $R^{6}_{T_3,K_4} = 0 \pm 0$
                $R^{6}_{T_3,K_5} = 0 \pm 0$ &
            $R^{6}_{T_4,K_1} = 0 \pm 0$
                $R^{6}_{T_4,K_2} = 0 \pm 0$
                $R^{6}_{T_4,K_3} = 0 \pm 0$
                $R^{6}_{T_4,K_4} = 0 \pm 0$
                $R^{6}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Thompson sampling &
            $R^{7}_{T_1,K_1} = 0 \pm 0$
                $R^{7}_{T_1,K_2} = 0 \pm 0$
                $R^{7}_{T_1,K_3} = 0 \pm 0$
                $R^{7}_{T_1,K_4} = 0 \pm 0$
                $R^{7}_{T_1,K_5} = 0 \pm 0$ &
            $R^{7}_{T_2,K_1} = 0 \pm 0$
                $R^{7}_{T_2,K_2} = 0 \pm 0$
                $R^{7}_{T_2,K_3} = 0 \pm 0$
                $R^{7}_{T_2,K_4} = 0 \pm 0$
                $R^{7}_{T_2,K_5} = 0 \pm 0$ &
            $R^{7}_{T_3,K_1} = 0 \pm 0$
                $R^{7}_{T_3,K_2} = 0 \pm 0$
                $R^{7}_{T_3,K_3} = 0 \pm 0$
                $R^{7}_{T_3,K_4} = 0 \pm 0$
                $R^{7}_{T_3,K_5} = 0 \pm 0$ &
            $R^{7}_{T_4,K_1} = 0 \pm 0$
                $R^{7}_{T_4,K_2} = 0 \pm 0$
                $R^{7}_{T_4,K_3} = 0 \pm 0$
                $R^{7}_{T_4,K_4} = 0 \pm 0$
                $R^{7}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        AdBandits &
            $R^{8}_{T_1,K_1} = 0 \pm 0$
                $R^{8}_{T_1,K_2} = 0 \pm 0$
                $R^{8}_{T_1,K_3} = 0 \pm 0$
                $R^{8}_{T_1,K_4} = 0 \pm 0$
                $R^{8}_{T_1,K_5} = 0 \pm 0$ &
            $R^{8}_{T_2,K_1} = 0 \pm 0$
                $R^{8}_{T_2,K_2} = 0 \pm 0$
                $R^{8}_{T_2,K_3} = 0 \pm 0$
                $R^{8}_{T_2,K_4} = 0 \pm 0$
                $R^{8}_{T_2,K_5} = 0 \pm 0$ &
            $R^{8}_{T_3,K_1} = 0 \pm 0$
                $R^{8}_{T_3,K_2} = 0 \pm 0$
                $R^{8}_{T_3,K_3} = 0 \pm 0$
                $R^{8}_{T_3,K_4} = 0 \pm 0$
                $R^{8}_{T_3,K_5} = 0 \pm 0$ &
            $R^{8}_{T_4,K_1} = 0 \pm 0$
                $R^{8}_{T_4,K_2} = 0 \pm 0$
                $R^{8}_{T_4,K_3} = 0 \pm 0$
                $R^{8}_{T_4,K_4} = 0 \pm 0$
                $R^{8}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        BESA &
            $R^{9}_{T_1,K_1} = 0 \pm 0$
                $R^{9}_{T_1,K_2} = 0 \pm 0$
                $R^{9}_{T_1,K_3} = 0 \pm 0$
                $R^{9}_{T_1,K_4} = 0 \pm 0$
                $R^{9}_{T_1,K_5} = 0 \pm 0$ &
            $R^{9}_{T_2,K_1} = 0 \pm 0$
                $R^{9}_{T_2,K_2} = 0 \pm 0$
                $R^{9}_{T_2,K_3} = 0 \pm 0$
                $R^{9}_{T_2,K_4} = 0 \pm 0$
                $R^{9}_{T_2,K_5} = 0 \pm 0$ &
            $R^{9}_{T_3,K_1} = 0 \pm 0$
                $R^{9}_{T_3,K_2} = 0 \pm 0$
                $R^{9}_{T_3,K_3} = 0 \pm 0$
                $R^{9}_{T_3,K_4} = 0 \pm 0$
                $R^{9}_{T_3,K_5} = 0 \pm 0$ &
            $R^{9}_{T_4,K_1} = 0 \pm 0$
                $R^{9}_{T_4,K_2} = 0 \pm 0$
                $R^{9}_{T_4,K_3} = 0 \pm 0$
                $R^{9}_{T_4,K_4} = 0 \pm 0$
                $R^{9}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for $9$ different algorithms on \textbf{problem 1} with different values of time $T$ and number of arm $K$.
    }
    \label{table:3:meanRegret_problem1}
\end{footnotesize}
\end{table}

\begin{table}[!t]
\begin{footnotesize}
    \centering
    \begin{tabular}{c|*{5}{m{2cm}}} % WARNING size ?
    \textbf{Algorithms} $\;$ \textbackslash $\;$ $\mathbf{T=}$
        & $T_1 = 1000$ & $T_2 = 5000$ & $T_3 = 10000$ & $T_4 = 50000$ \\
        \hline
        $\varepsilon$-greedy &
            $R^{1}_{T_1,K_1} = 0 \pm 0$
                $R^{1}_{T_1,K_2} = 0 \pm 0$
                $R^{1}_{T_1,K_3} = 0 \pm 0$
                $R^{1}_{T_1,K_4} = 0 \pm 0$
                $R^{1}_{T_1,K_5} = 0 \pm 0$ &
            $R^{1}_{T_2,K_1} = 0 \pm 0$
                $R^{1}_{T_2,K_2} = 0 \pm 0$
                $R^{1}_{T_2,K_3} = 0 \pm 0$
                $R^{1}_{T_2,K_4} = 0 \pm 0$
                $R^{1}_{T_2,K_5} = 0 \pm 0$ &
            $R^{1}_{T_3,K_1} = 0 \pm 0$
                $R^{1}_{T_3,K_2} = 0 \pm 0$
                $R^{1}_{T_3,K_3} = 0 \pm 0$
                $R^{1}_{T_3,K_4} = 0 \pm 0$
                $R^{1}_{T_3,K_5} = 0 \pm 0$ &
            $R^{1}_{T_4,K_1} = 0 \pm 0$
                $R^{1}_{T_4,K_2} = 0 \pm 0$
                $R^{1}_{T_4,K_3} = 0 \pm 0$
                $R^{1}_{T_4,K_4} = 0 \pm 0$
                $R^{1}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        Explore-then-Commit &
            $R^{2}_{T_1,K_1} = 0 \pm 0$
                $R^{2}_{T_1,K_2} = 0 \pm 0$
                $R^{2}_{T_1,K_3} = 0 \pm 0$
                $R^{2}_{T_1,K_4} = 0 \pm 0$
                $R^{2}_{T_1,K_5} = 0 \pm 0$ &
            $R^{2}_{T_2,K_1} = 0 \pm 0$
                $R^{2}_{T_2,K_2} = 0 \pm 0$
                $R^{2}_{T_2,K_3} = 0 \pm 0$
                $R^{2}_{T_2,K_4} = 0 \pm 0$
                $R^{2}_{T_2,K_5} = 0 \pm 0$ &
            $R^{2}_{T_3,K_1} = 0 \pm 0$
                $R^{2}_{T_3,K_2} = 0 \pm 0$
                $R^{2}_{T_3,K_3} = 0 \pm 0$
                $R^{2}_{T_3,K_4} = 0 \pm 0$
                $R^{2}_{T_3,K_5} = 0 \pm 0$ &
            $R^{2}_{T_4,K_1} = 0 \pm 0$
                $R^{2}_{T_4,K_2} = 0 \pm 0$
                $R^{2}_{T_4,K_3} = 0 \pm 0$
                $R^{2}_{T_4,K_4} = 0 \pm 0$
                $R^{2}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\mathrm{Exp}3^{++}$ &
            $R^3_{T_1,K_1} = 0 \pm 0$
                $R^3_{T_1,K_2} = 0 \pm 0$
                $R^3_{T_1,K_3} = 0 \pm 0$
                $R^3_{T_1,K_4} = 0 \pm 0$
                $R^3_{T_1,K_5} = 0 \pm 0$ &
            $R^3_{T_2,K_1} = 0 \pm 0$
                $R^3_{T_2,K_2} = 0 \pm 0$
                $R^3_{T_2,K_3} = 0 \pm 0$
                $R^3_{T_2,K_4} = 0 \pm 0$
                $R^3_{T_2,K_5} = 0 \pm 0$ &
            $R^3_{T_3,K_1} = 0 \pm 0$
                $R^3_{T_3,K_2} = 0 \pm 0$
                $R^3_{T_3,K_3} = 0 \pm 0$
                $R^3_{T_3,K_4} = 0 \pm 0$
                $R^3_{T_3,K_5} = 0 \pm 0$ &
            $R^3_{T_4,K_1} = 0 \pm 0$
                $R^3_{T_4,K_2} = 0 \pm 0$
                $R^3_{T_4,K_3} = 0 \pm 0$
                $R^3_{T_4,K_4} = 0 \pm 0$
                $R^3_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        $\UCB_1$ &
            $R^{4}_{T_1,K_1} = 0 \pm 0$
                $R^{4}_{T_1,K_2} = 0 \pm 0$
                $R^{4}_{T_1,K_3} = 0 \pm 0$
                $R^{4}_{T_1,K_4} = 0 \pm 0$
                $R^{4}_{T_1,K_5} = 0 \pm 0$ &
            $R^{4}_{T_2,K_1} = 0 \pm 0$
                $R^{4}_{T_2,K_2} = 0 \pm 0$
                $R^{4}_{T_2,K_3} = 0 \pm 0$
                $R^{4}_{T_2,K_4} = 0 \pm 0$
                $R^{4}_{T_2,K_5} = 0 \pm 0$ &
            $R^{4}_{T_3,K_1} = 0 \pm 0$
                $R^{4}_{T_3,K_2} = 0 \pm 0$
                $R^{4}_{T_3,K_3} = 0 \pm 0$
                $R^{4}_{T_3,K_4} = 0 \pm 0$
                $R^{4}_{T_3,K_5} = 0 \pm 0$ &
            $R^{4}_{T_4,K_1} = 0 \pm 0$
                $R^{4}_{T_4,K_2} = 0 \pm 0$
                $R^{4}_{T_4,K_3} = 0 \pm 0$
                $R^{4}_{T_4,K_4} = 0 \pm 0$
                $R^{4}_{T_4,K_5} = 0 \pm 0$ \\
        \hline
        \klUCB{} &
            $R^{5}_{T_1,K_1} = 0 \pm 0$
                $R^{5}_{T_1,K_2} = 0 \pm 0$
                $R^{5}_{T_1,K_3} = 0 \pm 0$
                $R^{5}_{T_1,K_4} = 0 \pm 0$
                $R^{5}_{T_1,K_5} = 0 \pm 0$ &
            $R^{5}_{T_2,K_1} = 0 \pm 0$
                $R^{5}_{T_2,K_2} = 0 \pm 0$
                $R^{5}_{T_2,K_3} = 0 \pm 0$
                $R^{5}_{T_2,K_4} = 0 \pm 0$
                $R^{5}_{T_2,K_5} = 0 \pm 0$ &
            $R^{5}_{T_3,K_1} = 0 \pm 0$
                $R^{5}_{T_3,K_2} = 0 \pm 0$
                $R^{5}_{T_3,K_3} = 0 \pm 0$
                $R^{5}_{T_3,K_4} = 0 \pm 0$
                $R^{5}_{T_3,K_5} = 0 \pm 0$ &
            $R^{5}_{T_4,K_1} = 0 \pm 0$
                $R^{5}_{T_4,K_2} = 0 \pm 0$
                $R^{5}_{T_4,K_3} = 0 \pm 0$
